---
title: "Partially observable predictor models for identifying cognitive markers"
date: "2025-02-19"
output:
  pdf_document:
    toc: true
  github_document:
    toc: true
    html_preview: false
editor_options:
  markdown:
    wrap: 72
---

These results belong to "Partially observable predictor models for identifying
cognitive markers" by Zita Oravecz, Martin Sliwinski, Sharon H. Kim, Lindy
Williams, Mindy J. Katz, and Joachim Vandekerckhove.

Note that due to randomness in the MCMC procedure, these results may not
exactly match the results in the paper.

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.path = "results_files/figure-gfm/"
)
library(here)
library(ggplot2)
library(knitr)
library(dplyr)
```

### Load processed results

```{r echo=TRUE}
results <- readRDS(here::here("tmp/processed_results.rds"))
```

### Define colors for models

```{r echo=TRUE}
model_colors <- c(
  "Manifest only" = "#009E73",
  "Manifest + latent descriptors" = "#E69F00",
  "Manifest + latent process" = "#0072B2"
)
```

### Cross-Validation Results

#### ROC Curves

```{r roc-plot, fig.width=8, fig.height=8}
ggplot() +
  geom_ribbon(data = results$ci_data,
              aes(x = FPR,
                  ymin = lower,
                  ymax = upper,
                  fill = Model,
                  group = Model),
              alpha = 0.2) +
  geom_line(data = results$plot_data,
            aes(x = FPR,
                y = TPR,
                color = Model,
                group = Model),
            size = 1) +
  geom_abline(intercept = 0,
              slope = 1,
              linetype = "dashed",
              color = "gray50") +
  scale_color_manual(values = model_colors) +
  scale_fill_manual(values = model_colors) +
  labs(x = "False positive rate",
       y = "True positive rate") +
  coord_equal() +
  theme_minimal() +
  theme(
    text = element_text(family = "serif", color = "black"),
    axis.title = element_text(size = 26, color = "black"),
    axis.text = element_text(size = 22, color = "black"),
    legend.title = element_text(size = 22, color = "black"),
    legend.text = element_text(size = 22, color = "black"),
    legend.position = c(0.975, 0.05),
    legend.justification = c(1, 0),
    legend.direction = "vertical",
    legend.box = "vertical",
    legend.margin = margin(t = 5, r = 5, b = 5, l = 5),
    legend.background = element_rect(fill = "white", color = NA),
    legend.box.background = element_rect(fill = "white", color = NA)
  )
```

#### AUC Results

```{r auc-table}
cv_table <- do.call(rbind,
                    lapply(results$cv_results,
                           function(res) {
                             data.frame(
                               Model = res$model,
                               AUC = sprintf("%.4f [%.4f, %.4f]",
                                             res$auc,
                                             res$ci_lower,
                                             res$ci_upper),
                               Folds = res$n_folds
                               )
                             }
                           )
                    )
kable(cv_table,
      caption = "Cross-validation AUC results with 95% confidence intervals")
```

### Full Information Results

#### Coefficient estimates for Manifest only
```{r fi-manifest, results='asis'}
if (!is.null(results$fi_results$manifest)) {
  df <- results$fi_results$manifest
  colnames(df) <- c("mean", "sd", "2.5%", "97.5%")
  kable(df, format = "pipe", digits = 4)
}
```

#### Coefficient estimates for Manifest + latent descriptors
```{r fi-descriptive, results='asis'}
if (!is.null(results$fi_results$descriptive)) {
  df <- results$fi_results$descriptive
  colnames(df) <- c("mean", "sd", "2.5%", "97.5%")
  kable(df, format = "pipe", digits = 4)
}
```

#### Coefficient estimates for Manifest + latent process
```{r fi-process, results='asis'}
if (!is.null(results$fi_results$process_model)) {
  df <- results$fi_results$process_model
  colnames(df) <- c("mean", "sd", "2.5%", "97.5%")
  kable(df, format = "pipe", digits = 4)
}
```
